---
title: "WriteFunctions(how = 'in R')"
author: "Thomas Huet, University of Oxford"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
```

## Functions in R: an overview

> "*There are only two hard things in Computer Science: cache invalidation and naming things*" -- Phil Karlton

Native functions

```{r addition, exercise=TRUE}
sum(1, 1)
```

Nested functions

```{r addition, exercise=TRUE}
df <- data.frame(
  blade = c("A", "B", "C", "D"),
  length = c(10.1, 0.82, 9.3, 7.4)
)
sum(mean(df$length), 1)
```

Help

```{r addition-h, exercise=TRUE}
?sum
```

## Exercices 1

### Fix the typo

```{r addition0, exercise=TRUE}
my_sum <- function(a, b){
  a + b
}

## here
my_sum(1, "1")
```

```{r addition0-solution}
my_sum(1, 1)
```

### Write the missing parameters

Write the missing parameters adding `1` and `2`

```{r addition1, exercise=TRUE}
my_sum <- function(a, b){
  a + b
}

## here
my_sum( , )
```

```{r addition1-solution}
my_sum(1, 2)
```

## Internal variables

Lorem

```{r varInter, exercise=TRUE}
my_loop <- function(a){
  for(i in a){
    print(i)
  }
}

## here
i <- "grey"
a <- c("red", "green", "blue", "orange")
my_loop(a)
print(i)
```

## Parameters

### Names

-   Give same names to variables outside the function and parameters inside the function (ex: `df`)

```{r varNames, exercise=TRUE}

df <- data.frame(
  blade = c("A", "B", "C", "D"),
  length = c(10.1, 0.82, 9.3, 7.4)
)

my_barplot <- function(df = NA){
  df_clean <- df[df$length > 4, ]
  g <- ggplot2::ggplot(df_clean, ggplot2::aes(x = blade, y = length)) + 
    ggplot2::geom_bar(stat = "identity", fill = "steelblue")
  return(g)
}

## here
my_barplot(df)
```

```{r varDefault-solution}
my_sum(1, 2)
```

### Default values

-   Assign default values to parameter when:
    -   the parameter/variable will be used more than once
    -   you know the function works with a precise dataset (ex: a TSV file) and values (ex: )

```{r varDefault, exercise=TRUE}

df <- data.frame(
  blade = c("A", "B", "C"),
  length = c(10.1, 8.2, 9.3)
)
color <- "steelblue"

my_barplot <- function(df = NA, color = "steelblue"){
  g <- ggplot2::ggplot(df, ggplot2::aes(x = blade, y = length)) + 
    ggplot2::geom_bar(stat = "identity", fill = color)
  return(g)
}

## here
my_barplot(df)
```

### Packages

-   Write the packages names explicitly within the function (ex: `ggplot2::`)

```{r varPackages, exercise=TRUE}

df <- data.frame(
  blade = c("A", "B", "C", "D"),
  length = c(10.1, 8.2, NA, "?"),
  stringsAsFactors = FALSE
)

my_barplot <- function(df = NA, 
                       color = "steelblue"){
  # only rows with numeric values
  df_clean <- df[!is.na(as.numeric(df$length)), ]
  # create the plot
  g <- ggplot2::ggplot(df_clean, ggplot2::aes(x = blade, y = length)) + 
    ggplot2::geom_bar(stat = "identity", fill = color)
  return(g)
}

## here
my_barplot(df)
```

```{r varPackages-solution}
# TODO: return the 3 places where the package name appears
```

## Function documentation

## DEBUG and troubleshouting

## Notes

-   syntax (spaces, `my_plot`)
-   `return`
-   `ggplot2::`
-   function call
-   where to place the comments `#`
-   `print` or `cat` inside a function
-   dataframe column names as variables

## Documentation

-   <https://tinystats.github.io/teacups-giraffes-and-statistics/01_introToR.html>

## About this document

This document is a Rmarkdown file using the `learnr` package
