---
title: "TEST"
# subtitle: "Create beautiful interactive slide decks with Reveal.js"
author: "zoometh"
# margin-left: 5.4mm
# margin-right: 5.4mm
format:
  revealjs: 
    slide-number: true
    chalkboard: true
    scrollable: true
    preview-links: auto
    logo: images/inst-uni-oxford_.png
    css: styles.css
    footer: <https://tinyurl.com/goa-oxford>
    # margin: 0
    # width: 1400
---

```{r, echo=FALSE}
library(shiny)
library(rmarkdown)
library(plotly)
library(ggtern)
library(plotly)
library(DT)
library(dplyr)
library(archdata)
```

## Conformity

::: {.panel-tabset}

### Processed

Processed data

```{r}
#| echo: false

data("Mesolithic")

Mesolithic.pers <- round(Mesolithic/rowSums(Mesolithic)*100, 1)

datatable(Mesolithic.pers, caption = "British Mesolithic assemblages (%)") %>%
  formatStyle(
    colnames(Mesolithic.pers),
    background = styleColorBar(Mesolithic.pers$Microliths, 'lightblue'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )
```


:::

::: footer
:::


## A classer

For I. Herzog, there is a difference between validation and verification: validation of the model is when it is consistent with the facts (BIB I. Herzog, S28-09, CAA 2016). 


"In short, identifying the existence of discrete cultural groups is not trivial." 
(Shennan et al. 2015)

chefferie simple
chefferie complexe: sites principiers: En moyenne une distance d’une centaine de kilomètres entre chacune de ces résidences

Test under the hypothesis H<sub>0</sub>. The *p-value* is the probability that H<sub>0</sub> is true, so the lower the *p-value*, the more likely H<sub>1</sub> is to exist<br>

## 💡

<div class="row">
<div class="column"><em><center>"people think closer things are more similar"</em><br><small> Montello and Fabrikant, 2006</small></center></div>
<div class="column">An archaeological culture is a polythetic assemblage of features more frequently associated with each other within a given area than outside it</div>
</div>

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```
