---
title: "TEST"
# subtitle: "Create beautiful interactive slide decks with Reveal.js"
author: "zoometh"
# margin-left: 5.4mm
# margin-right: 5.4mm
format:
  revealjs: 
    slide-number: true
    chalkboard: true
    scrollable: true
    preview-links: auto
    logo: images/inst-uni-oxford_.png
    css: styles.css
    footer: <https://tinyurl.com/goa-oxford>
    # margin: 0
    # width: 1400
---

```{r, echo=FALSE}
library(shiny)
library(rmarkdown)
library(plotly)
library(ggtern)
library(plotly)
library(DT)
library(dplyr)
```

## Conformity

::: {.panel-tabset}


### Regress


```{r}
#| warning: false
#| message: false
#| fig-width: 10

library(ggplot2)
library(archdata)
data("OxfordPots")

OxfordPots$OxfordPct.log <- log(OxfordPots$OxfordPct)
Oxford.water <- subset(OxfordPots, WaterTrans == 1)
lm.water <- lm(OxfordPct ~ OxfordDst, data = Oxford.water)
r2 <- round(summary(lm.water)$r.squared, 2)
Oxford.water$predicted <- predict(lm.water) 
Oxford.water$residuals <- residuals(lm.water)
values <- paste0("<b>", Oxford.water$Place, "</b><br>", 
                 "% Oxford Pottery (observed): ", Oxford.water$OxfordPct)
residuals <- paste0("<b>", Oxford.water$Place, "</b><br>",
                    "% Oxford Pottery (predicted): ", round(Oxford.water$predicted, 2))
m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 50,
  pad = 20
)
Oxford.water %>% 
  plot_ly(x = ~OxfordDst, width = 1200) %>% 
  add_trace(name = "Oxford Pottery", y = ~OxfordPct,
            #mode = 'scatter',
            marker = list(color = 'black'), 
            text = values,
            hoverinfo = 'text') %>%
  add_trace(name = "Predicted value", y = ~predicted, opacity = 0.5,
            #mode = 'scatter',
            marker = list(color = 'grey', line = list(color = 'grey', width = 1)),
            text = residuals,
            hoverinfo = 'text',
            visible = "legendonly") %>% 
  add_trace(name = "Regression line", x = ~OxfordDst, y = fitted(lm.water),
            mode = 'lines', line = list(color = 'black', width = 2),
            text = r2,
            hoverinfo = 'text',
            visible = "legendonly") %>%
  add_segments(name = "Residuals",  x = ~OxfordDst, y =  ~OxfordPct,
               xend = ~OxfordDst, yend = ~predicted, 
               mode = 'lines', 
               line = list(color = 'grey', width = 1, dash = 'dash'),
               text = ~residuals,
               hoverinfo = 'text',
               visible = "legendonly") %>%
  layout(title = paste0('Oxford pottery with a probable water transportation <br> (R<sup>2</sup> = ', r2, ")"),
         xaxis = list(title = "Distance (miles)"), 
         yaxis = list(title = "Percentage of Oxford Pottery"),
         margin = m,
         legend = list(orientation = "h",   
                       xanchor = "center",  
                       y = + 0.1,
                       x = 0.5))             
```


:::

::: footer
:::


## A classer

For I. Herzog, there is a difference between validation and verification: validation of the model is when it is consistent with the facts (BIB I. Herzog, S28-09, CAA 2016). 


"In short, identifying the existence of discrete cultural groups is not trivial." 
(Shennan et al. 2015)

chefferie simple
chefferie complexe: sites principiers: En moyenne une distance d’une centaine de kilomètres entre chacune de ces résidences

Test under the hypothesis H<sub>0</sub>. The *p-value* is the probability that H<sub>0</sub> is true, so the lower the *p-value*, the more likely H<sub>1</sub> is to exist<br>

## 💡

<div class="row">
<div class="column"><em><center>"people think closer things are more similar"</em><br><small> Montello and Fabrikant, 2006</small></center></div>
<div class="column">An archaeological culture is a polythetic assemblage of features more frequently associated with each other within a given area than outside it</div>
</div>

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```
